\documentclass[a4paper,12pt]{article}

\usepackage{style}

\begin{document}

\title{\textbf{Food Busters Prototype Mobile App Manual}}

\author{Nutthapat Pongtanyavichai, Developer of Food Busters}

\maketitle
\tableofcontents

\section{Disclaimer}

This is prototype app focuses on concept, interface \& UI, and basic logic flow of the app.
The goal of this prototype is to show the concept and test that concept with real users for feedback.
Some features are not properly implemented yet.
We will go along each features in this manual.

\section{Installation}

This prototype app by specification, supports from Android 5.
However, I recommend using Android 11 or later.
I need to inform you that we does not have many devices to do the testing.
We are sorry if the app doesn't work as intended for you.

\section{Download the App}

% todo Change download link to newer version
\begin{simplechar}
Download the apk file from the link \href{https://github.com/Food-Busters/food_busters/releases/download/1.0.301/food_busters-1.0.301-arm64-v8a.apk}{HERE} or scan below QR Code
\end{simplechar}

SPACE

HERE

IS

PLACE

HOLDER

FOR

QR

CODE

\textbf{Note}: The app is not signed, there may be a warning from Play Protect.

\section{Login \& Register}

As mention earlier that some features are not properly implemented with the reason given.
Login \& Register is one of them. \\

Any non-empty Username and Password will work here.

\section{Main Feature: SCAN}

Press Scan to enter Scan Menu

/* Images Here */

Based on current concept of our app, you will need to scan two times per meal,
\textbf{before} and \textbf{after} the meal. The AI \textit{(that doesn't exist yet)} will
process the images and gives you insight and analysis of your meal.

\section{Main Feature: POINTS \& REWARDS}

Points \& Rewards

\section{Main Feature: MY RECORD}

Record

\section{Main Feature: MISSIONS}

Missions

\section{Main Feature: LEADERBOARD}

Compete

\end{document}

